Lessons learned from bugs in models of human history

### 2020-06-10 paper.tex
Add note about mutation rates and thank JN.

The implementation of complex demographic models is error prone, and such errors
can have a large impact on downstream analyses and interpretation.
The discovery and correction of the demographic models discussed here underscore
how API design choice can lead to the propagation of mistakes that are difficult
to notice. We therefore recommend the following steps to ensure more robust simulations.

@@

\section*{Acknowledgements}
We would like to thank Alicia Martin for comments on the manuscript
and for providing the simulation data from~\cite{martin2017human}
used in Fig.~\ref{fig:prs}. We also like to thank
Chris Gignoux and Ilan Gronau for helpful comments on the manuscript.
JK would like to apologise
to those affected by the error in the example Out-of-Africa model and
by the poor design decisions in \msprime's demography API.

>>>>

The implementation of complex demographic models is error prone, and such errors
can have a large impact on downstream analyses and interpretation.
The discovery and correction of the demographic models discussed here underscore
how API design choice can lead to the propagation of mistakes that are difficult to notice.
There are myriad other ways to get models slightly or very wrong. Migration
rates can be set in the wrong direction, for example, and parameters can be
rescaled incorrectly when a new mutation rate is used.
We therefore recommend the following steps to ensure more robust simulations.

@@

\section*{Acknowledgements}
We would like to thank Alicia Martin for comments on the manuscript
and for providing the simulation data from~\cite{martin2017human}
used in Fig.~\ref{fig:prs}. We also like to thank
Chris Gignoux, Ilan Gronau and John Novembre for helpful comments on the manuscript.
JK would like to apologise
to those affected by the error in the example Out-of-Africa model and
by the poor design decisions in \msprime's demography API.
